---
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
  number_sections: true
 
title: ""
author: "[User-764Q](https://github.com/User-764Q)"
date: "`r paste0('Last Run: ', format(Sys.time(), '%A %d-%B-%Y'))`"
params: 
  param1: "Don't Forget about params"

---

<style>

#TOC {
 font-family: Calibri; 
 font-size: 16px;
 border-color: #3D68DF;
 background: #3D68DF;
}

body {
  font-family: Garamond;
  font-size: 16px; 
  border-color: #D0D0D0;
  background-color: #D0D0D0;
  color: #1A1A1A;
}

pre {
  color: #1A1A1A
  background: #D0D0D0;
  background-color: #D0D0D0
  font-family: Calibri; 
  
}

</style>

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(collapse = TRUE)

knitr::opts_chunk$set(warning = TRUE)

knitr::opts_chunk$set(message = TRUE)

knitr::opts_chunk$set(include = TRUE)

custom_black <- '1A1A1A'
custom_white <- 'C0C0C0'
custom_grey_dark <- '6F6F6F'
custom_grey_light <- 'B2B2B2'
custom_accent_blue <- '3D6BFF'

```

# Weibull Model 

## Introduction

Previously I have done some [unsophisticated analysis](https://rpubs.com/User764Q/820529) of the Alone TV show
But after doing the Datacamp [Sulvival Analysis in R]() course. I wanted to do something 
more sphisticated and formal. The key take away from the course was that the previous
analysis I did will under estimate the contestants survival as it is not known how long
the winners would have stayed on location if they didn't win. Survival analysis can account
for this and correct for the underestimation. 

Notes on how I created the data set are on my [previous post](https://rpubs.com/User764Q/820529)

For this post I want to;  

* compare the 'censored' vs 'uncensored' model I did previously (where 50% of 
contestants were gone after 40 days). 
* compare the two locations that have had wore than one season (Slave Lake and Vancouver Island), to see if they have significantly different survival 10th percentile, median and final percentile. 


## Loading Lbiraries and data     

```{r }

library(tidyverse)
library(survminer)
library(survival)

data <- read_csv("data.csv")

```

## Un-Censored Model

This analysis doesn't adjust for the fact that we don't know when the winners 
would have left. 

```{r}

wb <- survreg(Surv(DayLeft) ~ 1, data = data)

ten_pct_survival <- predict(wb, type = 'quantile', p = .1,
                                newdata = data.frame(1))

# median of patients survive beyond time point...
med_survival <- predict(wb, type = 'quantile', p = .5,
                                newdata = data.frame(1))

ninety_pct_survival <- predict(wb, type = 'quantile', p = .9, 
                               newdata  = data.frame(1))

```

Using the un-censored mode and considering all 8 seasons of Alone so far, it is 
expected 90% of consestants last **`r ten_pct_survival %>% round(0)`** days, 
half contestants last **`r med_survival %>% round(0)`** and 10% will last 
**`r ninety_pct_survival %>% round(0)`** days. 

## Censored Model

This analysis adjusts for the fact that we don't know when the winners 
would have left. 

```{r}

wb_cen <- survreg(Surv(DayLeft, Cens) ~ 1, data = data)

# 70 Percent of patients survive beyond time point...

ten_pct_survival_cen <- predict(wb_cen, type = 'quantile', p = .1,
                                newdata = data.frame(1))

# median of patients survive beyond time point...
med_survival_cen <- predict(wb_cen, type = 'quantile', p = .5,
                                newdata = data.frame(1))

ninety_pct_survival_cen<- predict(wb_cen, type = 'quantile', p = .9, 
                               newdata  = data.frame(1))

```

Using the un-censored mode and considering all 8 seasons of Alone so far, it is 
expected 90% of contestants last **`r ten_pct_survival_cen %>% round(0)`** days, 
half contestants last **`r med_survival_cen %>% round(0)`** and 10% will last 
**`r ninety_pct_survival_cen %>% round(0)`** days. 

## Comparing Locations



```{r}

data_bl <- data %>% 
  filter(Location %in% c('Vancouver-Is', 'Slave-Lk')) %>%
  mutate(Location = factor(Location))

wb_bl <- survreg(Surv(DayLeft, Cens) ~ Location, data = data_bl)

ninety_pct_survival_vi <- predict(wb_bl, type = 'quantile', 
                           p = .9, newdata = data.frame(Location = 'Vancouver-Is'))

med_survival_vi <- predict(wb_bl, type = 'quantile', 
                           p = .5, newdata = data.frame(Location = 'Vancouver-Is'))

ten_pct_survival_vi <- predict(wb_bl, type = 'quantile', 
                           p = .1, newdata = data.frame(Location = 'Vancouver-Is'))

wb_bl <- survreg(Surv(DayLeft, Cens) ~ Location, data = data_bl)

ninety_pct_survival_sl <- predict(wb_bl, type = 'quantile', 
                           p = .9, newdata = data.frame(Location = 'Slave-Lk'))

med_survival_sl <- predict(wb_bl, type = 'quantile', 
                           p = .5, newdata = data.frame(Location = 'Slave-Lk'))

ten_pct_survival_sl <- predict(wb_bl, type = 'quantile', 
                           p = .1, newdata = data.frame(Location = 'Slave-Lk'))

```

# Cox Model

The previous modelling assumes proportionate hazards. The Cox model also requires.The crossing survival curves I calculated earlier for the by location data means this may be an issue [Previous post](https://rpubs.com/User764Q/820529).

```{r}

cx_bl <- coxph(Surv(DayLeft, Cens) ~ Location, 
               data = data_bl)





```
